Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-02-24 paper/letter.tex
data update, M/L estimate

\begin{table}
\begin{center}
\begin{tabular}{lc}
$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
$\delta$(2000)$^{b}$ & -28d02m32s\\
$l$, $b$ (deg) & 294, 34\\
$m_V$ & 17.5\\
$v$(km s$^{-1}$) & 7795\\
M$_V$ & -17.6\\ 
Ly-$\alpha$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
Ly-$\alpha$ EW & $70$\AA\\
H$\beta$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$) & $1.62\times 10^{-14}$ \\
$21$cm (Jy km s$^{-1}$)& $<0.10$ \\
\end{tabular}
\end{center}
\caption{Basic observational characteristics of TOL1214-277
  \cite{Thuan97}\\} 
\end{table}

@@

The observed flux for the Lyman alpha line is $\sim
8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \cite{Thuan97}
and a Equivalent Width of $70$\AA and its H$\beta$ flux is 
$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
\cite{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of
4.9$\pm$0.1. 
Comparing this ratio with the theoretical expectation from case B
recombination of $23.3$ \cite{Hummer1987} one can estimate an escape
fraction of $20$\% for Ly$\alpha$ radiation.

@@

From this limit and the rotational velocity of $300$ km/s and the
limit in the size $D$ we have limits of for the dynamical mass of
$2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times 10^{9}$M$_{\odot}$.
which is at least $7$ to $25$ times larger than the H$I$ mass.

>>>>

\begin{table}
\begin{center}
\begin{tabular}{lc}
$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
$\delta$(2000)$^{b}$ & -28d02m32s\\
$l$, $b$ (deg) & 294, 34\\
$m_V$ & 17.5\\
M$_V$ & -17.6\\ 
$v$(km s$^{-1}$) & 7795\\
Ly-$\alpha$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
Ly-$\alpha$ EW & $70$\AA\\
H$\beta$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$) & $1.62\times 10^{-14}$ \\
$21$cm (Jy km s$^{-1}$)& $<0.10$ \\
\end{tabular}
\end{center}
\caption{Basic observational characteristics of TOL1214-277
  \cite{Thuan97}\\} 
\end{table}

@@

The observed flux for the Lyman alpha line is $\sim
8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \cite{Thuan97}
and a Equivalent Width of $70$\AA and its H$\beta$ flux is 
$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
\cite{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of
4.9$\pm$0.1. The Ly-$\alpha$ flux values correspond to luminosities of
$L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$ over a $20$\AA
bandwidth, which in turns translates  into a star formation rate of
$2.0$ M$_{\odot}$ yr$^{-1}$ using a standard conversion factor between
luminosity and star formation rate of $9.1\times 10^{-43}$
$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$. 
The absolute magnitude in the $V$ band translates into a luminosity of
$8.9\times 10^{8}$ L$_{\odot}$.
% using http://tomdwelly.com/tools_fluxtolum.php
Comparing this ratio with the theoretical expectation from case B
recombination of $23.3$ \cite{Hummer1987} one can estimate an escape
fraction of $20$\% for Ly$\alpha$ radiation.

@@

From this limit and the rotational velocity of $300$ km/s and the
limit in the size $D$ we have limits of for the dynamical mass of
$2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times 10^{9}$M$_{\odot}$.
which is at least $7$ to $25$ times larger than the H$I$ mass. The
mass to luminosity ratio is in turn between $2$ to $7$ times
$L_{\odot}/M_{\odot}$ considering the total luminosity in the $V$
band.
